---
title: "project model 3-Hierarchical clustering"
author: "Jingjing Li"
date: "2022-12-16"
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
---

I cannot knit all 3 clustering models at once, so I did them separately.

For Hierarchical clustering, I cannot generate PDF from RMarkdown file. 
I tried to troubleshoot using this website: https://yihui.org/tinytex/r/#debugging%20for%20debugging%20tip
and other websites, such as, stack overflow.

At the end, I found the issue is that there are invalid characters in the code that the 
LaTex cannot recognize, the character is the function fviz_dend.

Once I deleted the line with fviz_dend, I was able to generate PDF. However I need
the function.

At the end, I knit to Word document, then converted the Word file to PDF.

Helper packages

```{r}
library(tidyverse)
library(dplyr)
library(stringr)     
library(gridExtra)   
library(cluster)     
library(factoextra) 
library(mclust)
```

process the data
```{r}
df <-read.csv("radiomics_completedata.csv")

df <- na.omit(df)

df<-select(df,-c(Institution, Failure.binary))

set.seed(123)
```

Hierarchical clustering
```{r}
# Plot cluster results
p1 <- fviz_nbclust(df, FUN = hcut, method = "wss", 
                   k.max = 10) +
  ggtitle("(A) Elbow method")
p2 <- fviz_nbclust(df, FUN = hcut, method = "silhouette", 
                   k.max = 10) +
  ggtitle("(B) Silhouette method")
p3 <- fviz_nbclust(df, FUN = hcut, method = "gap_stat", 
                   k.max = 10) +
  ggtitle("(C) Gap statistic")

# Display plots side by side
gridExtra::grid.arrange(p1, p2, p3, nrow = 1)


d<- dist(df, method = "euclidean")
hc5 <- hclust(d, method = "ward.D2" )
dend_plot <- fviz_dend(hc5)#an warning
dend_data <- attr(dend_plot, "dendrogram")
dend_cuts <- cut(dend_data, h = 2)

# Ward's method
hc5 <- hclust(d, method = "ward.D2" )

# Cut tree into 4 groups
sub_grp <- cutree(hc5, k = 2)

# Number of members in each cluster
table(sub_grp)

# Plot full dendogram
fviz_dend(
  hc5,
  k = 2,
  horiz = TRUE,
  rect = TRUE,
  rect_fill = TRUE,
  rect_border = "jco",
  k_colors = "jco",
  cex = 0.1
)
```