---
title: "project model 2"
author: "Jingjing Li"
output: pdf_document
date: '2022-12-15'
---

## Helper packages

```{r}
library(keras)
library(caret)
library(rsample)   
library(recipes)   
library(h2o)      
```


load and process the data
```{r}
df = read.csv("radiomics_completedata.csv")

#splitting the data into training and testing
index<-createDataPartition(df$Failure.binary,p=0.7,list=F)

#Test labels in the Failure.binary column (column 2)
Train_Features <- data.matrix(df[index,-2])
Train_Labels <- df[index,2]
Test_Features <- data.matrix(df[-index,-2])
Test_Labels <- df[-index,2]
```

Convert the labels into categorical 
```{r}
to_categorical(as.numeric(Train_Labels))[,c(-1)] -> Train_Labels
to_categorical(as.numeric(Test_Labels))[,c(-1)] -> Test_Labels

#summary statistics
summary(Train_Labels)

#printing the structures of the dataset
str(Train_Features)
```

Convert the features into matrix 
```{r}
as.matrix(apply(Train_Features, 2, function(x) (x-min(x))/(max(x) - min(x)))) -> Train_Features
as.matrix(apply(Test_Features, 2, function(x) (x-min(x))/(max(x) - min(x)))) -> Test_Features
```

Build the model

```{r}
model <- keras_model_sequential()

model %>%
  layer_dense(units = 256, activation = "sigmoid", input_shape = ncol(Train_Features)) %>%
  layer_dropout(rate = 0.25) %>% 
  
  layer_dense(units = 128, activation = "sigmoid") %>%
  layer_dropout(rate = 0.25) %>% 
  
  layer_dense(units = 128, activation = "sigmoid") %>%
  layer_dropout(rate = 0.25) %>% 
  
  layer_dense(units = 64, activation = "sigmoid") %>%
  layer_dropout(rate = 0.25) %>%
  
  layer_dense(units = 2, activation = "softmax")

summary(model)

```

Backpropagation compiler approach (slide 15)
```{r}
compile(loss = "categorical_crossentropy",
                  optimizer = optimizer_rmsprop(),
                  metrics = c('accuracy'))
```

compiler approach (slide 33)
```{r}
model %>% compile(
          loss = "categorical_crossentropy",
          optimizer = optimizer_adam(),
          metrics = c("accuracy"))
```

train the model with epoch=10, batch size=128 and validation split=0.15
```{r}
history <- model %>% 
  fit(Train_Features,Train_Labels, epochs = 10, batch_size = 128, validation_split = 0.15)

plot(history)
```

Evaluate the trained model using the testing dataset. 
```{r}
model %>% evaluate(Test_Features,Test_Labels)
```

Get the model prediction using the testing dataset.
```{r}
model %>%
  predict_classes(Test_Feature)
```














